RProtoBuf: Efficient Cross-Language Data Serialization in R

### 2014-01-03 papers/rjournal/eddelbuettel-francois-stokely.Rnw
Add a JSSwrapper around the same content used for the RJournal article.  Edits should still be made to the same eddelbuettel-francois-stokely.Rnw file, and the Makefile still only builds the RJournal version by default, but now you can type pdflatex JSSwrapper instead and manually see what it would look like when formatted for JSS instead.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@687 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\subsection{Importing Message Descriptors from \texttt{.proto} files}

@@

R booleans can accept three values: \texttt{TRUE}, \texttt{FALSE}, and
\texttt{NA}.  However, most other languages, including the protocol
buffer schema, only accept \text{TRUE} or \text{FALSE}.  This means
that we simply can not store R logical vectors that include all three
possible values as booleans.  The library will refuse to store
\texttt{NA}s in protocol buffer boolean fields, and users must instead
choose another type (such as integers) capable of storing three
distinct values.

@@

% N.B. see table.Rnw for how this table is created.
%
% latex table generated in R 3.0.2 by xtable 1.7-0 package
% Fri Dec 27 17:00:03 2013
\begin{table}[ht]
\begin{center}
\scalebox{0.9}{
\begin{tabular}{l|r|r|r|r|r}
  \hline
Data Set & object.size & \multicolumn{2}{c|}{R Serialization} &
\multicolumn{2}{c}{RProtoBuf Serialization} \\
 & & Default & gzipped & Default & gzipped \\
  \hline
uspop & 584.00 & 268 & 172 & 211 & 148 \\
  Titanic & 1960.00 & 633 & 257 & 481 & 249 \\
  volcano & 42656.00 & 42517 & 5226 & 42476 & 4232 \\
  euro.cross & 2728.00 & 1319 & 910 & 1207 & 891 \\
  attenu & 14568.00 & 8234 & 2165 & 7771 & 2336 \\
  ToothGrowth & 2568.00 & 1486 & 349 & 1239 & 391 \\
  lynx & 1344.00 & 1028 & 429 & 971 & 404 \\
  nottem & 2352.00 & 2036 & 627 & 1979 & 641 \\
  sleep & 2752.00 & 746 & 282 & 483 & 260 \\
  co2 & 4176.00 & 3860 & 1473 & 3803 & 1453 \\
  austres & 1144.00 & 828 & 439 & 771 & 410 \\
  ability.cov & 1944.00 & 716 & 357 & 589 & 341 \\
  EuStockMarkets & 60664.00 & 59785 & 21232 & 59674 & 19882 \\
  treering & 64272.00 & 63956 & 17647 & 63900 & 17758 \\
  freeny.x & 1944.00 & 1445 & 1311 & 1372 & 1289 \\
  Puromycin & 2088.00 & 813 & 306 & 620 & 320 \\
  warpbreaks & 2768.00 & 1231 & 310 & 811 & 343 \\
  BOD & 1088.00 & 334 & 182 & 226 & 168 \\
  sunspots & 22992.00 & 22676 & 6482 & 22620 & 6742 \\
  beaver2 & 4184.00 & 3423 & 751 & 3468 & 840 \\
  anscombe & 2424.00 & 991 & 375 & 884 & 352 \\
  esoph & 5624.00 & 3111 & 548 & 2240 & 665 \\
  PlantGrowth & 1680.00 & 646 & 303 & 459 & 314 \\
  infert & 15848.00 & 14328 & 1172 & 13197 & 1404 \\
  BJsales & 1632.00 & 1316 & 496 & 1259 & 465 \\
  stackloss & 1688.00 & 917 & 293 & 844 & 283 \\
  crimtab & 7936.00 & 4641 & 713 & 1655 & 576 \\
  LifeCycleSavings & 6048.00 & 3014 & 1420 & 2825 & 1407 \\
  Harman74.cor & 9144.00 & 6056 & 2045 & 5861 & 2070 \\
  nhtemp & 912.00 & 596 & 240 & 539 & 223 \\
  faithful & 5136.00 & 4543 & 1339 & 4936 & 1776 \\
  freeny & 5296.00 & 2465 & 1518 & 2271 & 1507 \\
  discoveries & 1232.00 & 916 & 199 & 859 & 180 \\
  state.x77 & 7168.00 & 4251 & 1754 & 4068 & 1756 \\
  pressure & 1096.00 & 498 & 277 & 427 & 273 \\
  fdeaths & 1008.00 & 692 & 291 & 635 & 272 \\
  euro & 976.00 & 264 & 186 & 202 & 161 \\
  LakeHuron & 1216.00 & 900 & 420 & 843 & 404 \\
  mtcars & 6736.00 & 3798 & 1204 & 3633 & 1206 \\
  precip & 4992.00 & 1793 & 813 & 1615 & 815 \\
  state.area & 440.00 & 422 & 246 & 405 & 235 \\
  attitude & 3024.00 & 1990 & 544 & 1920 & 561 \\
  randu & 10496.00 & 9794 & 8859 & 10441 & 9558 \\
  state.name & 3088.00 & 844 & 408 & 724 & 415 \\
  airquality & 5496.00 & 4551 & 1241 & 2874 & 1294 \\
  airmiles & 624.00 & 308 & 170 & 251 & 148 \\
  quakes & 33112.00 & 32246 & 9898 & 29063 & 11595 \\
  islands & 3496.00 & 1232 & 563 & 1098 & 561 \\
  OrchardSprays & 3600.00 & 2164 & 445 & 1897 & 483 \\
  WWWusage & 1232.00 & 916 & 274 & 859 & 251 \\
   \hline
\end{tabular}
}
\caption{Serialization sizes with R's built-in serialization and
  RProtoBuf for 50 sample R datasets.}
\label{tab:compression}
\end{center}
\end{table}

@@

\address{Dirk Eddelbuettel\\
  Debian and R Projects\\
  711 Monroe Avenue, River Forest, IL 60305\\
  USA}
\email{edd@debian.org}

\address{Murray Stokely\\
  Google, Inc.\\
  1600 Amphitheatre Parkway\\
  Mountain View, CA 94043\\
  USA}
\email{mstokely@google.com}

>>>>

\subsection{Importing Message Descriptors from .proto files}

@@

R booleans can accept three values: \texttt{TRUE}, \texttt{FALSE}, and
\texttt{NA}.  However, most other languages, including the protocol
buffer schema, only accept \texttt{TRUE} or \texttt{FALSE}.  This means
that we simply can not store R logical vectors that include all three
possible values as booleans.  The library will refuse to store
\texttt{NA}s in protocol buffer boolean fields, and users must instead
choose another type (such as integers) capable of storing three
distinct values.

@@

% N.B. see table.Rnw for how this table is created.
%
% latex table generated in R 3.0.2 by xtable 1.7-0 package
% Fri Dec 27 17:00:03 2013
\begin{table}[h!]
\begin{center}
\scalebox{0.9}{
\begin{tabular}{l|r|r|r|r|r}
  \hline
Data Set & object.size & \multicolumn{2}{c|}{R Serialization} &
\multicolumn{2}{c}{RProtoBuf Serialization} \\
 & & Default & gzipped & Default & gzipped \\
  \hline
uspop & 584.00 & 268 & 172 & 211 & 148 \\
  Titanic & 1960.00 & 633 & 257 & 481 & 249 \\
  volcano & 42656.00 & 42517 & 5226 & 42476 & 4232 \\
  euro.cross & 2728.00 & 1319 & 910 & 1207 & 891 \\
  attenu & 14568.00 & 8234 & 2165 & 7771 & 2336 \\
  ToothGrowth & 2568.00 & 1486 & 349 & 1239 & 391 \\
  lynx & 1344.00 & 1028 & 429 & 971 & 404 \\
  nottem & 2352.00 & 2036 & 627 & 1979 & 641 \\
  sleep & 2752.00 & 746 & 282 & 483 & 260 \\
  co2 & 4176.00 & 3860 & 1473 & 3803 & 1453 \\
  austres & 1144.00 & 828 & 439 & 771 & 410 \\
  ability.cov & 1944.00 & 716 & 357 & 589 & 341 \\
  EuStockMarkets & 60664.00 & 59785 & 21232 & 59674 & 19882 \\
  treering & 64272.00 & 63956 & 17647 & 63900 & 17758 \\
  freeny.x & 1944.00 & 1445 & 1311 & 1372 & 1289 \\
  Puromycin & 2088.00 & 813 & 306 & 620 & 320 \\
  warpbreaks & 2768.00 & 1231 & 310 & 811 & 343 \\
  BOD & 1088.00 & 334 & 182 & 226 & 168 \\
  sunspots & 22992.00 & 22676 & 6482 & 22620 & 6742 \\
  beaver2 & 4184.00 & 3423 & 751 & 3468 & 840 \\
  anscombe & 2424.00 & 991 & 375 & 884 & 352 \\
  esoph & 5624.00 & 3111 & 548 & 2240 & 665 \\
  PlantGrowth & 1680.00 & 646 & 303 & 459 & 314 \\
  infert & 15848.00 & 14328 & 1172 & 13197 & 1404 \\
  BJsales & 1632.00 & 1316 & 496 & 1259 & 465 \\
  stackloss & 1688.00 & 917 & 293 & 844 & 283 \\
  crimtab & 7936.00 & 4641 & 713 & 1655 & 576 \\
  LifeCycleSavings & 6048.00 & 3014 & 1420 & 2825 & 1407 \\
  Harman74.cor & 9144.00 & 6056 & 2045 & 5861 & 2070 \\
  nhtemp & 912.00 & 596 & 240 & 539 & 223 \\
  faithful & 5136.00 & 4543 & 1339 & 4936 & 1776 \\
  freeny & 5296.00 & 2465 & 1518 & 2271 & 1507 \\
  discoveries & 1232.00 & 916 & 199 & 859 & 180 \\
  state.x77 & 7168.00 & 4251 & 1754 & 4068 & 1756 \\
  pressure & 1096.00 & 498 & 277 & 427 & 273 \\
  fdeaths & 1008.00 & 692 & 291 & 635 & 272 \\
  euro & 976.00 & 264 & 186 & 202 & 161 \\
  LakeHuron & 1216.00 & 900 & 420 & 843 & 404 \\
  mtcars & 6736.00 & 3798 & 1204 & 3633 & 1206 \\
  precip & 4992.00 & 1793 & 813 & 1615 & 815 \\
  state.area & 440.00 & 422 & 246 & 405 & 235 \\
  attitude & 3024.00 & 1990 & 544 & 1920 & 561 \\
  randu & 10496.00 & 9794 & 8859 & 10441 & 9558 \\
  state.name & 3088.00 & 844 & 408 & 724 & 415 \\
  airquality & 5496.00 & 4551 & 1241 & 2874 & 1294 \\
  airmiles & 624.00 & 308 & 170 & 251 & 148 \\
  quakes & 33112.00 & 32246 & 9898 & 29063 & 11595 \\
  islands & 3496.00 & 1232 & 563 & 1098 & 561 \\
  OrchardSprays & 3600.00 & 2164 & 445 & 1897 & 483 \\
  WWWusage & 1232.00 & 916 & 274 & 859 & 251 \\
   \hline
\end{tabular}
}
\caption{Serialization sizes with R's built-in serialization and
  RProtoBuf for 50 sample R datasets.}
\label{tab:compression}
\end{center}
\end{table}

@@
